Self Regulation Ontology Retest Analyses

### 2018-04-27 code/SRO_Retest_Analyses.Rmd
playing around with sem ci s for each subject

```{r}
get_ind_ci = function(dv_var){
  matched = match_t1_t2(dv_var)
  grand_mean = mean(matched$score)
  grand_sd = sd(matched$score)
  dv_icc = get_icc(dv_var)
  sep = grand_sd * sqrt(1-dv_icc^2)
  matched = matched %>% 
    spread(time, score) %>%
    rename("t1"="1", "t2"="2") %>%
    mutate(true_score = grand_mean+dv_icc*(t1-grand_mean),
           ci_up = true_score+sep,
           ci_low = true_score-sep,
           t2_out_ci = ifelse(t2>ci_up|t2<ci_low,1,0),
           prop_dist = abs(t1-t2)/sep,
           large_dist = ifelse(prop_dist>1,1,0))
    return(matched)
}

@@

get_ind_ci("five_facet_mindfulness_survey.total")
```

>>>>

Here I calculate the proportion of subjects that move more than one standard error of prediction (SEP) in t2 compared to t1 for each measure.

This is odd to think about because the larger the ICC of a measure the smaller the SEP. So very small differences between the two time points can be categorized as 'meaningful' based on the tiny SEP.

```{r}
get_ind_ci = function(dv_var){
  matched = match_t1_t2(dv_var)
  grand_mean = mean(matched$score)
  grand_sd = sd(matched$score)
  dv_icc = get_icc(dv_var)
  sep = grand_sd * sqrt(1-(dv_icc^2))
  matched = matched %>% 
    spread(time, score) %>%
    rename("t1"="1", "t2"="2") %>%
    mutate(true_score = grand_mean+(dv_icc*(t1-grand_mean)),
           ci_up = true_score+(1.96*sep),
           ci_low = true_score-(1.96*sep),
           t2_out_ci = ifelse((t2>ci_up)|(t2<ci_low),1,0))
    return(matched)
}

@@

get_ind_ci("ten_item_personality_survey.extraversion")
```
